Advanced Calc Homework 2 \large 1.3.4, 1.3.7, 1.3.14, 2.1.2a, 2.1.6, 2.1.7, 2.1.15a

### 2017-02-02 311/latex/HW2.tex

@@

\section{Problem 2.1.7}
We want to show that $\exists N$ such that $\forall n \geq N$, $a_n > 0$.\\

>>>>

\section{Problem 1.3.14}
We want to show the relation $ab \leq \frac12\left(a^2+b^2\right)$. for any $a,b\in\mathbb{R}$\\

Note that since the square of any real number is nonnegative, $\left(a-b\right) \geq 0$. Squaring both sides yields $a^2 + b^2 - 2ab \geq 0$, and so $ab \leq \frac12\left(a^2+b^2\right$, as desired.\\

@@

\section{Problem 2.1.6}
We want to show that $\exists N$ such that $\forall n \geq N$, $a_n > 0$.\\
